Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-02 Doc/Miccai/simulation.tex
spell check
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@388 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
modifs in simulation.tex (rest shape control)
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@394 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

We present a new approach that overcomes these difficulties by performing topological changes on the mesh to connect shell elements along joining edges (see figure \ref{fig-JoiningVessels}). Since there is a certain distance between two joining edges in general, a topological modification alters the shape and size of affected shell elements. Note that in this simulation state there is temporarily no correlation to reality. We then start a controlled relaxation process during which the shell elements progressivly converge to their energetical equilibrium. To keep the simulation stable we avoid a strong increase in internal forces by linearly interpolate the rest shape of the connected mesh to the initial rest shape before joining. The effect is similar to contracting springs but there is no such problem like surplus energy after the joining process is done.

>>>>

We present a new approach that overcomes these difficulties by performing topological changes on the mesh to connect shell elements along joining edges (see figure \ref{fig-JoiningVessels}). Since there is a certain distance between two joining edges in general, a topological modification alters the shape and size of affected shell elements. 
Both actual shape $\myvec{x}$ and rest shape $\myvec{x_0}$ of these shells are modified.
Note that in this simulation state there is temporarily no correlation to reality. 
We then start a controlled relaxation process during which the shell elements progressively converge to their energetical equilibrium
(i.e. we progressively re-contract the rest shape of the shells to their initial value while the simulation compute the positions of the whole mesh).
To keep the simulation stable we avoid a strong increase in internal forces by linearly interpolate the rest shape of the connected mesh to the initial rest shape before joining. 
The effect is similar to contracting springs but there is no such problem like surplus energy after the joining process is done.
